The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-09-18 paper2_JNLS/paper.tex
NM

>>>>

Briefly, consider the parameter $\lamfac$, the number of characteristic wavelengths in the physical domain. We require $\lamfac \le \Lambda$, so that the mode $\uhat_{\lamfac}$ corresponding to the physical wavelength $\lambda$ is resolved. In the case $\lamfac = \Lambda$, $\lambda$ corresponds to the smallest resolved wavelength. Often, we will choose $\lamfac = \Lambda$ or $\Lambda/2$.
